openarchaeoCollaboration

### 2022-04-27 analysis/paper.Rmd
Add interactive graph vis.
Cite {gh}

That is, for each project in open-archaeo with a GitHub repository, we added information on individual contributors, commits, issues, etc. from the API.

@@

>>>>

That is, for each project in open-archaeo with a GitHub repository, we added information on individual contributors, commits, issues, etc. from the API using the R package `gh` [@gh].

@@

```{r iplot-graph-repo-repo}
iplot <- oarch_graph_repo_repo |>
    ggraph(layout = "graphopt") +
    geom_edge_link(aes(alpha = n)) +
    geom_point_interactive(aes(x, y, colour = category, tooltip = repo)) + 
    scale_edge_alpha(trans = "log") +
    labs(edge_alpha = "Common contributors") +
    theme_graph()

girafe(ggobj = iplot)
```
